---
title: "Converting WB Data"
output: html_document
---

```{r cars}
setwd("C:/Users/wb413533/Box Sync/Competitive Cities (Non-shared Working Copies)/Datasources for Updating Master Dataset/WDI_csv")

all_WB_data <- read.csv('WDI_Data.csv', header = TRUE, na.strings = "")


names(all_WB_data)

summary(all_WB_data$x2012)

str(all_WB_data)

head(all_WB_data)


```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
setwd("C:/Users/wb413533/Downloads")
#loading some json
library(jsonlite)
library(RJSONIO)
library(rjson)

founders_data <- fromJSON("479646_founders.json")
JsonData <- fromJSON(file = "196809_founders.json" )
thirdfounder <- fromJSON(file = "728857_founders.json")

names(lapply(thirdfounder[[2]][[2]],print))


length(JsonData[[2]])



lapply(JsonData[[2]],print)


lapply(JsonData[[2]][[1]],print)


university_search <- function(script, key_word){
  script_length <- nchar(script)
  key_word_add <- nchar(key_word)-1
  appearance_number <- 0
  for (i in 1:script_length){
    if((i + key_word_add <= script_length) & (substr(script,i,i+ key_word_add) == key_word)){
      appearance_number <- appearance_number + 1
    }
    
  }
  if(appearance_number > 0){
    return ("Went to University")
  }
}

university_search("hello hello asd;lfkja;ldskf","hello")

substr("hello hello asd;lfkja;ldskf",7,11) == "hello"

nchar("hello")-1



#role, founder, ended, started_at, type, id, image, angellist_url, follower_count, bio,id, community_profile, thum_url, logo_url, high_concept, created_at, product_desc, community_profile, quality 

for(file in example_files){
  print (file)
}

```



Testing basic looping with lists on the founders' information
```{r}

#rm(list = ls())
setwd("C:/Users/wb413533/Box Sync/Competitive Cities (Non-shared Working Copies)/startups")
library(jsonlite)
library(RJSONIO)
library(rjson)


list_founders <- list.files()

test_list <- list_founders[1:10]


load_lists <- function(list_of_names){
    number_of_lists <- length(list_of_names)
    array_of_lists <- list()
    for(name in list_of_names){
      temp_founder <- fromJSON(file = name)
      array_of_lists <- c(array_of_lists, list(temp_founder))
    
    }

  return(array_of_lists)

}

example_lists <- load_lists(test_list)

#so now to access info about founder use:
#example_lists[[1]][[2]][[1]][[4]]
#founder bio: example_lists[[1]][[2]][[1]][[4]][[7]]


#startup info: example_lists[[1]][[2]][[1]][[8]]
#high concept... example_lists[[1]][[2]][[1]][[8]][[14]]


#How many don't have information on founders, etc.

total_lists <- load_lists(list_founders)

check_founder_info <- function(founders){
  total_number_of_companies <- length(founders)
  number_with_info <- 0
  index_with_info <- numeric()
  for(idx in 1:total_number_of_companies){
    if(length(founders[[idx]][[2]]) >0){
      number_with_info <- number_with_info + 1
      index_with_info <- c(index_with_info, idx)
    }
  
  }
  return(index_with_info)
}

print (check_founder_info(total_lists)) #7003!

founders_with_info <- check_founder_info(total_lists)

7003/10875

check_if_advisor <- function(founders){
  total_number_of_companies <- length(founders)
  number_advisors <- 0
  for(idx in 1:total_number_of_companies){
    if(founders[[idx]][[1]] > 0 & founders[[idx]][[1]] == length(founders[[idx]][[2]])){
      for(jdx in 1:founders[[idx]][[1]]){
          if(founders[[idx]][[2]][[jdx]][[1]] == "advisor" ){
          number_advisors <- number_advisors + 1
          print (number_advisors)
          }
      }
    }
  
  }
  return(number_advisors)
}

check_if_advisor(total_lists)

#checking how many files have a mnumber of founders, but has no details about the company/founders
check_gaps <- function(founders){
  total_number_of_companies <- length(founders)
  number_gaps <- 0
  index_gaps <- numeric()
  for(idx in 1:total_number_of_companies){
    if(founders[[idx]][[1]] > 0){
      if(length(founders[[idx]][[2]])==0){
          number_gaps <- number_gaps + 1
          index_gaps <- c(index_gaps, idx)
      }
    }
  
  }
  return(number_gaps)
}

print (check_gaps(total_lists)) #2480 json files has some founders listed, but no detailed informatoin


#checking Education file

check_education <- function(founders){
  total_number_of_companies <- length(founders)
  id_row_num <- 0
  id_vector <- numeric()
  education <- numeric()
  for(idx in 1:total_number_of_companies){
    if(founders[[idx]][[1]] > 0){
      if(length(founders[[idx]][[2]]) !=0){
          for(jdx in 1:length(founders[[idx]][[2]])){
            if(!is.null(founders[[idx]][[2]][[jdx]][[4]][[7]])){
              if(grepl("College", founders[[idx]][[2]][[jdx]][[4]][[7]])){
                id_vector <- c(id_vector,founders[[idx]][[2]][[jdx]][[4]][[3]])
                }
              }
          }
      }
    }
  
  }
  return(id_vector)
}

print (check_education(total_lists))




test_load <- fromJSON(file = "1000047_founders.json")

empty_list <- list()

get_roles <- function(founders){
  total_number_of_companies <- length(founders)
  roles <- character()
  for(idx in 1:total_number_of_companies){
    if(founders[[idx]][[1]] > 0 & founders[[idx]][[1]] == length(founders[[idx]][[2]])){
      for(jdx in 1:founders[[idx]][[1]]){
          roles <- c(roles, founders[[idx]][[2]][[jdx]][[1]])
      }
    }
  
  }
  return(roles)
}

print(get_roles(total_lists))

```


Extracting Founders' Data from Json Files
```{r}

#obtaining founder_data form one file. Using Once tested with one file, 
#will iterate through all of the folders and files in the fodler

json_string_founder <- read_file("63_founders.json")


test_founder <- fromJSON(file = "63_founders.json")


temp_part <- json_string_founder%>%
  enter_object('startup_roles')%>%
  gather_array%>%
  spread_values(role = jstring('role'), merge_id = jnumber('id'))%>%
  enter_object('tagged')%>%
  spread_values(founder_name = jstring('name'), founder_id = jnumber('id'), 
                founder_follower = jnumber('follower_count'),
                bio = jstring('bio'))

temp_part2 <- json_string_founder%>%
   enter_object('startup_roles')%>%
   gather_array%>%
   spread_values(role = jstring('role'), merge_id =jnumber('id'))%>%
   enter_object('startup')%>%
   spread_values(startup_id = jnumber('id'))

founder_info <- right_join(temp_part, temp_part2, by = c('merge_id'))
names(founder_info)
final_output <- founder_info%>%
  select(startup_id,founder_name,founder_id,founder_followers,bio)


```

```{r}


#just set the appropriate working directory that has all of the founder info, and then run the function below
#no inputs necessar, the first lines will obtain the names of folders and the names of the files

#takes about 45 minutes to run...
founder_company_connection <- function(){
  
  vector_of_json_files <- list.files()
  founder_data_frame <- data.frame(startup_id =numeric(),
                 founder_name = character(),
                 founder_id = numeric(),
                 founder_followers = numeric(),
                 bio =character())
  
  for(temp_json in vector_of_json_files){
    temp_founder_1 <- temp_json%>%
      enter_object('startup_roles')%>%
      gather_array%>%
      spread_values(role = jstring('role'), merge_id = jnumber('id'))%>%
      enter_object('tagged')%>%
      spread_values(founder_name = jstring('name'), founder_id = jnumber('id'), 
                    founder_followers = jnumber('follower_count'),
                    bio = jstring('bio'))

    temp_founder_2 <- temp_json%>%
      enter_object('startup_roles')%>%
      gather_array%>%
      spread_values(role = jstring('role'), merge_id =jnumber('id'))%>%
      enter_object('startup')%>%
      spread_values(startup_id = jnumber('id'))

    founder_info <- right_join(temp_founder_1, temp_founder_2, by = c('merge_id'))
    final_output <- founder_info%>%
      select(startup_id,founder_name,founder_id,founder_followers,bio)
    
    founder_data_frame <- rbind(founder_data_frame, final_output)
  }
  return(founder_data_frame)
}

all_available_founders <- founder_company_connection()

#setwd(....) 

#Need to resetworking directory to the appropriate place. The previous function changed
#the working directory as necessary.
write.csv(all_available_founders,"founder_info.csv")


```

Structure: list of 5 lists
[[1]] - Total number of founders
[[2]] - Startup_roles - contains info on founders
  [[1]] - List of 9 variables about first founder
    [[1]] - role
    [[2]] - ended_at
    [[3]] - started_at
    [[4]] - info about first founder (7 variables)
      [[1]] - name
      [[2]] - type
      [[3]] - id
      [[4]] - image
      [[5]] - angellist_url
      [[6]] - follower_count
      [[7]] - bio
    [[5]] - id
    [[6]] - title
    [[7]] - confirmed
    [[8]] - info about the startup (14 variables)
      [[1]] - hidden
      [[2]] - created_at
      [[3]] - id
      [[4]] - follower_count
      [[5]] - quality
      [[6]] - name
      [[7]] - updated_at
      [[8]] - company_url
      [[9]] - community_profile
      [[10]] - product_desc
      [[11]] - thumb_url
      [[12]] - angellist_url
      [[13]] - logo_url
      [[14]] - high_concept
    [[9]] - created_at    
  [[2]] - List of 9 variables about second founder
    ......
[[3]] - page
[[4]] - per_page
[[5]] - last_page

